Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-05-02 ba_resubmit/response_to_reviewers2.tex

\reply{%
	When writing, I believed it was sufficient to include the superscripts on the $m$ and $u$ in the definition of $w$. However, you are correct, it is more clear to explicitly include it on the $w$. This has been updated. 
}

\pointRaised{R}{%
Gamma is in some places described as a set and in others as a matrix (particularly in
sections 4.2 and 5.1).
}

\reply{%
	$\Gamma$ is a matrix comprised by comparison vectors. It is certainly not a set in the mathematical sense. All references to $\Gamma$ as a set have been removed.

	{\color{red}{I found one example of me saying that $\Gamma$ is ''comprised of the set of comparison vectors.' I'll triple check before resubmission.}}
}

\pointRaised{R}{%
Section 4.3, second paragraph, the definitions of the concatenated vectors $\alpha_0$ and $\beta_0$
should have final elements subscripted by $L_f$, where the sub-subscript is capitalized.}

\reply{%
	You are correct. This has been revised. 
}

\end{document}
